### 2018-07-11 paper/sphinxes.tex
Sphinxes: index at zero, shortens comments, wide figures

\Cref{fig:CreateHeader} summarizes the algorithm.

@@

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Require{%
      $I\in \bin^\kappa$ is an identifier.
      $L = \{N_0, \dotsc, N_\nu\}$ such that $N_i, N_j\subset \N$, $N_i\cap N_j 
      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
      $N_\nu$ is the destination.
    }
    \Function{\CreateHeader}{$I, L$}
      \State $w_L\gets \max_{N\in L} |N|$
      \Comment{Maximum width of a layer, \ie alternative nodes.}
      \State $w_H\gets (2w_L+2)$
      \Comment{Header width:
        layer nodes' ciphertexts and addresses ($2w_L\kappa$),
        address of next node ($\kappa$),
        \ac{MAC} ($\kappa$).}
      \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
      b_\nu)\gets \ComputeKeys[L, w_L]$
      \State $\phi_1, \dotsc, \phi_\nu\gets \ComputePadding[\{s_1, \dotsc, 
      s_\nu\}, w_H]$
      \State $\alpha \gets \alpha_\nu$
      \State $C\gets C_\nu$
      \State $\beta \gets
      \left\{\left\{N_\nu\concat
          I\concat
          0_{(2w_L(r-\nu)+2)\kappa}\right\} \oplus
        \prg(\hash_\prg(s_\nu)_{[0..(2w_L(r-\nu)+3)\kappa-1]}\right\}\concat 
      \phi_\nu$
      \Comment{$\beta_\nu$}
      \State $\gamma \gets $
      \Comment{$\gamma_\nu$}
      \For{$\nu-1\leq i\leq 1$}
        \State $(\alpha, C, \beta, \gamma) \gets
          \WrapHeader[i, (\alpha, \beta, \gamma), \alpha_i, s_i, C_i, N_{i+1}, 
          w_L]$
      \EndFor
    \EndFunction

    \Function{\WrapHeader}{$i, (\alpha_{i+1}, \beta_{i+1}, \gamma_{i+1}), 
      \alpha_i, s_i, C_i, N_{i+1}, w_L$}
      \If{$i < 1$}
        \Return $\bot$
      \EndIf
      \State $\beta_i \gets \{N_{i+1}, \concat \gamma_{i+1}\concat 
      (\beta_{i+1})_{[0..(w_L r-1)\kappa -1]}\}$
      \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
      \Return $i-1, (\alpha_i, C_i, \beta_i, \gamma_i)$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:CreateHeader}%
    \dots
  }
\end{figure}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Function{\ComputeKeys}{$L = \{L_1, \dotsc, L_l\}, w_L$}
      \State $\sk\rgets \ZZ_q^*, \pk\gets g^\sk$
      \State $\alpha_0\gets \pk$
      \State $s_0\rgets \bin^\kappa$
      \Comment{Differs from Sphinx.}
      \For{$1\leq i\leq |N_0|$}
        \State $s_0^{(i)}\gets \pk_{n_i}^\sk$, where $n_i\in |N_0|$.
        \State $c_0^{(i)}\gets \Enc[_{s_0^{(i)}}][s_0]$
      \EndFor
      \For{$|N_0|+1\leq i\leq w_L$}
        \State $c_0^{(i)}\rgets \bin^\kappa$
      \EndFor
      \State $C_0\gets (c_0^{(1)}, \dotsc, c_0^{(w)})$
      \State $b_0\gets \hash_\blind(\alpha_0, s_0)$
      \Comment{Same as Sphinx.}
      \For{$1\leq i < \nu$}
        \State Compute $(\alpha_i, C_i, \beta_i, \gamma_i)$ as follows.
        \State $\alpha_i = \pk^{b_{i-1}}$
        \State $s_i\rgets \bin^\kappa$
        \Comment{Differs from Sphinx.}
        \For{$1\leq j\leq |N_i|$}
          \State $s_i^{(j)}\gets \pk_{n_j}^\sk$, where $n_j\in |N_i|$.
          \State $c_i^{(j)}\gets \Enc[_{s_i^{(j)}}][s_i]$
        \EndFor
        \For{$|N_i|+1\leq i\leq w_L$}
          \State $c_0^{(i)}\rgets \bin^\kappa$
        \EndFor
        \State $C_i\gets (c_i^{(1)}, \dotsc, c_i^{(w)})$
        \Comment{Same as Sphinx.}
        \State $b_i\gets \hash_\blind(\alpha_i, s_i)$
      \EndFor
      \State \Return $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, 
      C_\nu, b_\nu)$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:SphinxesKeys}%
    \dots
  }
\end{figure}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Function{\ComputePadding}{$\{s_1, \dotsc, s_\nu\}, w_H$}
      \State $\phi_1\gets \epsilon$
      \Comment{$\epsilon$ is the empty string.}
      \For{$2\leq i\leq \nu$}
        \State $\phi_i = \{ \phi_{i-1}\concat 0_{w_H} \} \oplus
          \{ \prg(\hash_\prg(s_{i-1}))_{[(w_H(r-i+1)+3)\kappa..(w_H 
            r+3)\kappa-1]} \}$
      \EndFor
      \State \Return $\phi_1, \dotsc, \phi_\nu$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:SphinxesPadding}%
    \dots
  }
\end{figure}

>>>>

\Cref{fig:CreateHeader} summarizes the algorithm.
\(w_L\) is the maximum width of a layer, \ie alternative nodes.
\(w_H\) is the header width:
layer nodes' ciphertexts and addresses ($2w_L\kappa$),
address of next node ($\kappa$),
\ac{MAC} ($\kappa$).

@@

\begin{figure*}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Function{\CreateHeader}{$I, L$}
      \State $w_L\gets \max_{N\in L} |N|$
      \Comment{Layer width}
      \State $w_H\gets (2w_L+2)$
      \Comment{Header width}
      \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
      b_\nu)\gets \ComputeKeys[L, w_L]$
      \State $\phi_0, \dotsc, \phi_\nu\gets \ComputePadding[\{s_0, \dotsc, 
      s_\nu\}, w_H]$
      \State $\alpha \gets \alpha_\nu$
      \State $C\gets C_\nu$
      \State $\beta \gets
      \left\{\left\{N_\nu\concat
          I\concat
          0_{(2w_L(r-\nu)+2)\kappa}\right\} \oplus
        \prg(\hash_\prg(s_\nu)_{[0..(2w_L(r-\nu)+3)\kappa-1]}\right\}\concat 
      \phi_\nu$
      \Comment{$\beta_\nu$}
      \State $\gamma \gets \mac(\hash_\mac(s_\nu), \beta)$
      \Comment{$\gamma_\nu$}
      \For{$\nu-1\leq i\leq 1$}
        \State $(\alpha, C, \beta, \gamma) \gets
          \WrapHeader[i, (\alpha, \beta, \gamma), \alpha_i, s_i, C_i, N_{i+1}, 
          w_L]$
      \EndFor
      \State \Return $(\alpha, C, \beta, \gamma)$
    \EndFunction

    \Function{\WrapHeader}{$i, (\alpha_{i+1}, \beta_{i+1}, \gamma_{i+1}), 
      \alpha_i, s_i, C_i, N_{i+1}, w_L$}
      \If{$i < 0$}
        \Return $\bot$
      \EndIf
      \State $\beta_i \gets \{N_{i+1}, \concat \gamma_{i+1}\concat 
      (\beta_{i+1})_{[0..(w_L r-1)\kappa -1]}\}$
      \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
      \State \Return $i-1, (\alpha_i, C_i, \beta_i, \gamma_i)$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:CreateHeader}%
    \dots
      $I\in \bin^\kappa$ is an identifier.
      $L = \{N_0, \dotsc, N_\nu\}$ such that $N_i, N_j\subset \N$, $N_i\cap N_j 
      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
      $N_\nu$ is the destination.
  }
\end{figure*}

\begin{figure*}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Function{\ComputeKeys}{$L = \{L_0, \dotsc, L_l\}, w_L$}
      \State $\sk\rgets \ZZ_q^*, \pk\gets g^\sk$
      \State $\alpha_0\gets \pk$
      \State $s_0\rgets \bin^\kappa$
      \For{$1\leq i\leq |N_0|$}
        \State $s_0^{(i)}\gets \pk_{n_i}^\sk$, where $n_i\in |N_0|$.
        \State $c_0^{(i)}\gets \Enc[_{s_0^{(i)}}][s_0]$
      \EndFor
      \For{$|N_0|+1\leq i\leq w_L$}
        \State $c_0^{(i)}\rgets \bin^\kappa$
      \EndFor
      \State $C_0\gets (c_0^{(1)}, \dotsc, c_0^{(w)})$
      \State $b_0\gets \hash_\blind(\alpha_0, s_0)$
      \For{$1\leq i < \nu$}
        \State Compute $(\alpha_i, C_i, \beta_i, \gamma_i)$ as follows.
        \State $\alpha_i = \pk^{b_{i-1}}$
        \State $s_i\rgets \bin^\kappa$
        \For{$1\leq j\leq |N_i|$}
          \State $s_i^{(j)}\gets \pk_{n_j}^\sk$, where $n_j\in |N_i|$.
          \State $c_i^{(j)}\gets \Enc[_{s_i^{(j)}}][s_i]$
        \EndFor
        \For{$|N_i|+1\leq i\leq w_L$}
          \State $c_0^{(i)}\rgets \bin^\kappa$
        \EndFor
        \State $C_i\gets (c_i^{(1)}, \dotsc, c_i^{(w)})$
        \State $b_i\gets \hash_\blind(\alpha_i, s_i)$
      \EndFor
      \State \Return $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, 
      C_\nu, b_\nu)$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:SphinxesKeys}%
    \dots
  }
\end{figure*}

\begin{figure*}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Function{\ComputePadding}{$\{s_0, \dotsc, s_\nu\}, w_H$}
      \State $\phi_0\gets \epsilon$
      \Comment{$\epsilon$ is the empty string.}
      \For{$1\leq i\leq \nu$}
        \State $\phi_i = \{ \phi_{i-1}\concat 0_{w_H} \} \oplus
          \{ \prg(\hash_\prg(s_{i-1}))_{[(w_H(r-i)+3)\kappa..(w_H 
            r+3)\kappa-1]} \}$
      \EndFor
      \State \Return $\phi_0, \dotsc, \phi_\nu$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:SphinxesPadding}%
    \dots
  }
\end{figure*}
